% LaTeX resume using res.cls
\documentclass[line,10pt]{res}
\title{Resume}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.9in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.13in}     % space between header and text
\setlength{\headheight}{13.6pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}Daniel N. Hill} % force lhead all the way left
\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document

\begin{document} 
\thispagestyle{empty} % this page does not have a header
\name{Daniel N. Hill}
\address{716.771.8224}
\address{daniel.n.hill@gmail.com}

\begin{resume}

\section{EXPERIENCE}
\vspace{5pt}

{\bf Research Scientist}, 2023-present \\ Meta Reality Labs, Burlingame, CA 
  \begin{itemize}
          \item[] Developing machine learning algorithms for neural wristband technology and brain-computer interfaces that enable control of devices through neural signals.
          \item[] Working on consumer BCI hardware to translate neural activity into digital interactions.
          \item[] Advancing the intersection of neuroscience and machine learning for next-generation human-computer interaction.
   \end{itemize}

{\bf Senior Applied Scientist}, 2018-2023 \\ Amazon.com, Search, Berkeley, CA 
  \begin{itemize}
          \item[] Led team of scientists and engineers to personalize query autocomplete and product search results via deep learning and extreme multilabel ranking models. Held full ownership of team's production goals and science roadmap.
          \item[] Managed multi-team collaborations to enable use of in-session signals at inference time.
          \item[] Mentored applied scientist interns leading to 4 conference publications with 1 in review.
   \end{itemize}
 {\bf Applied Scientist}, 2015-2018 \\ Amazon.com, Personalization, Palo Alto, CA 
  \begin{itemize}
          \item[] Developed ranking algorithms that incorporate multi-armed bandits, diversification, and personalization. Ranking improvements led to an annualized business impact of over \$200 MM.
          \item[] Designed and implemented the engine for a multivariate testing system in which experiments with over 100 treatments converge 10x faster than traditional A/B testing. Platform is used for high-throughput experimentation by teams across multiple orgs.
   \end{itemize}
   
 {\bf Senior Data Scientist}, 2013-2015 \\ Integral Ad Science, New York, NY 
  \begin{itemize}
          \item[] Led science for ``Causal Impact'' project to estimate return-on-investment of digital ad campaigns when A/B tests are unavailable. Work resulted in a new product launch.
        \end{itemize}

 {\bf Post-doctoral fellow}, 2010-2012 \\ Technical University of Munich, Munich, Germany 
  \begin{itemize}
          \item[] Imaging of synaptic activity in mouse motor cortex.
        \end{itemize}


\section{EDUCATION}
\vspace{5pt}
 {\bf Computational Neuroscience, PhD}, 2009 \\  University of California, San Diego
  \begin{itemize}
          \item[] Studied sensorimotor relationship between rat whisker behavior, facial muscle activity, and spike activity in primary motor cortex. 
          \item[] Developed rig to simultaneously combine video, electromyography (EMG), and extracellular spike recordings in the awake rat.
          \item[] Published UltraMegaSort2000 spike sorting software for identifying individual spike trains in extracellular electrode recordings.
   \end{itemize}

 {\bf Electrical and Computer Engineering, MS}, 2008 \\ University of California, San Diego
  \begin{itemize}
          \item[] Specialized in signal processing and control theory.
   \end{itemize}

 {\bf Computer Science, BS}, 2002 \\ Rochester Institute of Technology
   \begin{itemize}
          \item[] Specialized in artificial intelligence.
   \end{itemize}

\section{SKILLS} 
\vspace{5pt}

{\bf Programming:} Python, PyTorch, Java, Spark, Git, \LaTeX, bash, docker, HTML, AWS \\
{\bf Machine Learning: } Recommender systems, personalization, deep learning, multi-armed bandits, natural langauge processing, extreme multilabel ranking, gradient-boosted decision trees
    
\section{SELECTED MACHINE LEARNING PUBLICATIONS} 
\vspace{5pt}

Block A, Kidambi R, \textbf{Hill DN}, Joachims T, Dhillon IS. Counterfactual Learning to Rank for Utility Maximizing Query Autocompletion. SIGIR (2022)

Sen R, Rakhlin A, Ying L, Kidambi R, Fostesr D, \textbf{Hill DN}, Dhillon IS. Top-k eXtreme Contextual Bandits with Arm Hierarchy.  ICML. (2021)

Yadav N, Sen R, \textbf{Hill DN}, Mazumdar A, Dhillon IS. Session-Aware Query Auto-completion using Extreme Multi-label Ranking.  KDD. (2021)

Ai Q, \textbf{Hill DN}, Vishwanathan SVN, Croft WB. A Zero Attention Model for Personalized Product Search. CIKM. (2019)

\textbf{Hill DN}, Nassif H, Liu Y, Iyer A, Vishwanathan SVN. An efficient bandit algorithm for realtime multivariate optimization. KDD. (2017) \textbf{Winner of Audience Appreciation Award.}


\section{SELECTED NEUROSCIENCE PUBLICATIONS} 
\vspace{5pt}

\textbf{Hill DN}, Curtis J, Moore JD, Kleinfeld D.  Primary motor cortex reports efferent control of vibrissa position on multiple timescales. Neuron. 72(2):344-56 (2011).

\textbf{Hill DN}, Mehta SB, Kleinfeld D.  Quality metrics to accompany spike sorting of extracellular signals. J. Neurosci. 31:8699-8705 (2011)

\textbf{Hill DN}, Bermejo R, Zeigler HP, Kleinfeld D. Biomechanics of the vibrissa motor plant in rat: Rhythmic whisking consists of triphasic neuromuscular activity. J Neurosci. 28(13):3438-55 (2008). 



\end{resume}
\end{document}






























